---
title: "caribouRSF_NT"
author: ""
date: "05 December 2020"
output: pdf_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hold")
```

# Overview

This module runs the NT1 caribou RSF prepared by DeMars et al (2020). When no parameters are changed and no inputs are provided (i.e. Time, fire layers, disturbance layers), the module replicates DeMars work. This module can also be used for RSF forecasting, if right inputs are provided. 

# Usage

```{r module_usage}
install.packages("Require")
library("Require")
Require("SpaDES.core")

# setwd("~/Path/To/Directory/ProjectFolder") # uncommenting here lets you set a specific path

# The suggested folder structure is:
# ProjectFolder  -- modules -- caribouRSF_NT 
#               |
#                -- inputs
#               |
#                -- outputs
#               |
#                -- cache
# This structure allows one to add more modules with time.

setPaths(modulePath = checkPath(file.path(getwd(), "modules"), create = TRUE), 
         cachePath = checkPath(file.path(getwd(), "cache"), create = TRUE), 
         inputPath = checkPath(file.path(getwd(), "inputs"), create = TRUE), 
         outputPath = checkPath(file.path(getwd(), "outputs"), create = TRUE))
# When the directories are created, place the folder 'caribouRSF_NT' in the folder 'modules'

getPaths() # shows where the 4 relevant paths are

times <- list(start = 2017, end = 2017)

parameters <- list(
  "simulationProcess" = "static",
  "cropRSFToShp" = TRUE, # Set this to FALSE (default) if you don't want the projection to be cropped
  "yearsToSaveCaribouLayers" = 2017,
  "predictLastYear" = FALSE
)

# ATTENTION: If you downloaded the module (instead of forking from GitHub, you might need to rename the directory, currently (i.e. 'caribouRSF_NT-main') back to its original name (i.e. 'caribouRSF_NT').
modules <- list("caribouRSF_NT")

## OBJECTS ##
# Here we provide the raster that should be used as the template (mainly for resolution and projection), names `rasterToMatch`, as well as the study area (`studyArea`) that we want to crop our results to. As a test,
# I provide here a small study area in the NWT, within NT1. However, the code for the NT1 study area is   

studyArea <- Cache(prepInputs, targetFile = "Edehzhie.shp",
                  alsoExtract = "similar",
                  url = "https://drive.google.com/open?id=1VP91AyIeGCFwJS9oPSEno4_SbtJQJMh7",
                  destinationPath = Paths$inputPath,
                  userTags = c("outFun:Cache",
                               "step:prepEdehzhie"))
Edehzhie$Name <- Edehzhie$NAME_1

rasterToMatch <- Cache(prepInputs, targetFile = "EOSD_covType.tif",
                                      archive = "EOSD_covType.zip",
                                      alsoExtract = "similar",
                                      url = "https://drive.google.com/file/d/16Eha9ZOToUszHln4UtOl6f6Qs-br1_l0/view?usp=sharing",
                                      studyArea = studyArea,
                                      destinationPath = Paths$inputPath,
                                      filename2 = "rasterToMatch",
                                      fun = "raster::raster",
                                      userTags = c("outFun:Cache", "step:prepRTM"))

objects <- list(studyArea = studyArea,
                rasterToMatch = rasterToMatch)

caribouRSF <- simInitAndSpades(times = times,
                               params = parameters,
                               modules = modules,
                               objects = objects, debug = 1, 
                               cache = TRUE)

```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE}
df_params <- moduleParams("caribouRSF_NT", "..")
knitr::kable(df_params)
```

# Outputs  

To explore the outputted RSF map, the coefficients used, and the layers that generated the maps, please use:

```{r outputs, echo = FALSE}
caribouRSF$predictedPresenceProbability
caribouRSF$coeffTablAndValues
caribouRSF$caribouLayers
```
